Finite Complete Suites for CSP Refinement Testing

### 2019-04-14 scp-journal/article-revision-1/main.tex
First changes regading reviewer 1

Since we have finite complete CSP test suites, it is useful for the first
time to calculate how many test executions are needed when using them.
Previous work did not consider sufficient conditions for finiteness, so
complexity was not a concern. We answer the following questions. (1)~What is
the worst-case bound on the number of test executions to be performed to
verify an SUT with respect to failures refinement, when we use our test
suite? (2)~What is the worst-case bound for traces refinement? (3)~Is it
possible to reduce the maximal length of traces when testing for failures or
traces refinement? We consider the first question~(1) in
Section~\ref{section:complexity:failures}, where we also discuss whether  
it is possible to reduce the number of test executions with a different test
suite.  With the answer to question~(1), question~(2) is a fairly simple
consequence we discuss briefly at the end of 
Section~\ref{section:complexity:failures}. Question~(3) is the subject of
Section~\ref{section:complexity:length}.

@@

$Q$, however, neither conforms to $P$ in the failures refinement relation,
nor in the traces-refinement relation. This can only be seen when executing
the test $U_F(pq-1)$ and $U_T(pq-1)$, respectively. These tests fail, so this
shows that $P\not\lessdet_F Q$ and $P\not\lessdet_T Q$ according to
Theorem~\ref{th:failurestest} and Theorem~\ref{th:tracetest}. Moreover, this
shows that the maximal trace length $pq$ to be investigated in the tests
cannot be further reduced without losing the completeness property of the
test suites. \xbox
\end{example}
%
Generalising Example~\ref{ex:pq}, it can be shown that for any $p,q \geq 2$,
%\in\mathbb{N}$,
there exist reference processes $P$ with $p$ states and implementation
processes $Q$ with $q$ states, such that a violation of the traces-refinement
property can only be detected with a trace of length $pq$. This is proven in
the following
theorem. %In the proof, we use the processes $P$ and $Q$ introduced in Example~\ref{ex:pq}.

>>>>

With finite complete CSP test suites test suites at hand, it is now possible 
to calculate how many test executions are needed when using them.
Previous work did not consider sufficient conditions for finiteness, so
estimates for the maximal number 
of executions could not be calculated. 
We answer the following questions. (1)~What is
the worst-case bound on the number of test executions to be performed to
verify an SUT with respect to failures refinement, when we use our test
suite? (2)~What is the worst-case bound for traces refinement? (3)~Is it
possible to reduce the maximal length of traces when testing for failures or
traces refinement? We consider the first question~(1) in
Section~\ref{section:complexity:failures}, where we also discuss whether  
it is possible to reduce the number of test executions with a different test
suite.  With the answer to question~(1), question~(2) is a fairly simple
consequence we discuss briefly at the end of 
Section~\ref{section:complexity:failures}. Question~(3) is the subject of
Section~\ref{section:complexity:length}.

@@

$Q$, however, neither conforms to $P$ in the failures refinement relation,
nor in the traces-refinement relation. This can only be seen when executing
the test $U_F(pq-1)$ and $U_T(pq-1)$, respectively. These tests fail, because
they allow for execution of the following trace of length 12
$$
s_\text{fail} = a.a.a.b.a.a.a.b.a.a.a.b
$$
Only in the very last step, the final $b$-event can be produced by $Q$ but is refused by $P$.
Therefore, tests $U_F(11)$ and $U_T(11)$ enter their first branch (\ref{eq:ufa}) and (\ref{eq:uta}), respectively,\ when engaging into the last $b$, and this produces the $\efail$-event and shows  that $P\not\lessdet_F Q$ and $P\not\lessdet_T Q$ according to
Theorem~\ref{th:failurestest} and Theorem~\ref{th:tracetest}.. The tests 
$U_F(j)$ and $U_T(j)$ with $j < pq-1 = 11$ only execute true prefixes of $s_\text{fail}$ which 
are allowed for $P$, so that these tests pass.

This
shows that the maximal trace length $pq$ to be investigated in the tests
cannot be further reduced without losing the completeness property of the
test suites. \xbox
\end{example}
%
Generalising Example~\ref{ex:pq}, it can be shown that for any $p,q \geq 2$,
%\in\mathbb{N}$,
there exist reference processes $P$ with $p$ states and implementation
processes $Q$ with $q$ states, such that a violation of the traces-refinement
property can only be detected with a trace of length $pq$. This is proven in
the following
theorem. %In the proof, we use the processes $P$ and $Q$ introduced in Example~\ref{ex:pq}.
